\documentclass[times, 11pt, a4paper]{article}
\usepackage{tikz}
\usepackage{caption} 
\captionsetup[table]{skip=10pt}
\usepackage{needspace} 
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[para]{threeparttable}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{tipa}
\usepackage{amssymb,amsmath,bm}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{url}
\usepackage{float}
%\usepackage{llncsdoc}
\usepackage[top=1.5in, bottom=1.5in, left=1.2in,right=1in]{geometry}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{verbatim}
\usepackage{enumitem}
\usetikzlibrary{shapes,arrows}
\setcounter{secnumdepth}{3}
\setlist{nolistsep}
\linespread{1.25}
\textheight 8.8in
\textwidth 6.2in

\def\vec#1{\ensuremath{\bm{{#1}}}}
\def\mat#1{\vec{#1}}


\sloppy % better line breaks
%\ninept
\begin{document}
%\begin{frontmatter}
\input{title.tex}
\thispagestyle{empty}
\newpage
\thispagestyle{empty}
%\addcontentsline{toc}{section}{References}
\tableofcontents
\newpage
\setcounter{page}{1}

\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, text width=5em, text centered, rounded corners]
\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
\tikzstyle{block1} = [draw, fill=blue!20, rectangle, 
    minimum height=3em, text width=7em, text centered, rounded corners]
\tikzstyle{decision} = [draw, fill=blue!20, diamond, 
    minimum width=3cm, minimum height=1cm, text centered, aspect=1.5]
\tikzstyle{arrow} = [thick,->,>=stealth]    

\Needspace{5\baselineskip}

\section{Introduction} \label{Introduction}
This is introduction section

\Needspace{5\baselineskip}
\section{Literature Review}
Literature survey


\Needspace{5\baselineskip}

\section{Motivation}
Motivation

\Needspace{5\baselineskip}

\section{Work Done}
ggg 
\subsection{Robust GCI detection for Human voice}
gdgd

\subsubsection{Pre-processing}
\Needspace{5\baselineskip}

\section{Summary and Conclusion}

tessr

\Needspace{5\baselineskip}
\section{Future Work}
\begin{enumerate}
\item Exploring suitable signal processing methods to extract accurate melody from singing voice.
\item Exploring appropriate source separation methods to extract the vocal signals.
\item Applications
\begin{itemize}
	\item \textbf{Sargam learning tool for Indian classical music:} Sargam in Indian Music refers to singing of notes. While learning Indian music, this tool will help in providing suggestions on the note rendered by a trainee.
	\item \textbf{Automatic tanpura tuner:} In a rendition, tanpura is tuned to the base frequency of the singer manually. Instead an automatic tuner system is developed which plays tanpura based on the base frequency of the singer.
	\item \textbf{Tonic independent melody comparison:} Tonic refers to the base pitch chosen by the singer to explore the full pitch range comfortably. 			When the same melody is sung in different voices, there is a large difference in pitch contour between both the melodies. Tonic normalizes the two 					melodies 	to cents scale for comparison. We attempt the remove the need of tonic in melody comparison.

\end{itemize}

\end{enumerate}

\Needspace{5\baselineskip}

\section*{Publications} 
\begin{itemize}
\item \textbf{Conference}
	\begin{itemize}
	 	\item[--]  Pradeep Rengaswamy, Gurunath Reddy M,  K. Sreenivasa Rao,  and Pallab Dasgupta``\textit{A Robust Non-Parametric and Filtering Based Approach for Glottal Closure Instant Detection,"} in \textit{INTERSPEECH 2016}. (Accepted).
	 	\end{itemize}
\end{itemize}
	 

\Needspace{5\baselineskip}

\section*{Acknowledgements}
The present work is carried out under the project entitled "\textit{Scientific Approach to Networking and Designing of Heritage Interfaces} (\textbf{SANDHI})" sponsored by Ministry of Human Resource Development (MHRD), Govt. of India.

\newpage
\bibliographystyle{plain}
\bibliography{Ref}
\end{document}	